AI Safety for High Energy Physics

### 2019-10-04 documentation/manuscript.tex
added FGSM plots

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{figures/FGSM_Significance.pdf}\\
\includegraphics[width=0.4\textwidth]{figures/FGSM_D2.pdf}
\caption{Top: The relative discovery significance (true positive rate / square root of false positive rate) as a function of the classifier threshold for HL observables and LL observables before and after the FGSM attack described in Sec.~\ref{subsec:fgsm}.  Bottom: the $D_2$ observable before and after the FGSM attack for signal and background. }
\label{fig:FGSM2}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{figures/FGSM_Significance.pdf}
\caption{Top: The relative discovery significance (true positive rate / square root of false positive rate) as a function of the classifier threshold for HL observables and LL observables before and after the FGSM attack described in Sec.~\ref{subsec:fgsm}.  Bottom: the $D_2$ observable before and after the FGSM attack for signal and background. }
\label{fig:FGSM2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{figures/FGSM/FGSM_NN_LL.pdf}
\includegraphics[width=0.4\textwidth]{figures/FGSM/FGSM_NN_HL.pdf}
\includegraphics[width=0.4\textwidth]{figures/FGSM/FGSM_pT.pdf}
\includegraphics[width=0.4\textwidth]{figures/FGSM/FGSM_mass.pdf}
\includegraphics[width=0.4\textwidth]{figures/FGSM/FGSM_D2.pdf}
\caption{The classifier output and various observables before and after the FGSM attack for signal and background. }
\label{fig:FGSM2}
\end{figure}
